---
title: "README"
author: "Henry Hu"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Installation instructions

To install this package from GitHub to Rstudio, RTools and devtools are required to be installed. Run the following code on the Console.

```{r}
devtools::install_github("Henryhuhuhu/RPackage")
```

## RSA Package

This package contains the functions that will encode messages using the RSA methodology. These functions include:

-   RSAPrimeGenerate(*n*) - The random prime number generator of an inputted bit size *n* that outputs a prime number of the provided bit size.

-   RSAGenerateKey(*p*, *q*) - The key encryption function which needs the input of two unique large prime integers *p* and *q* to generate the public and private keys.

-   RSAEncrypt(*plaintext*, *e*, *n*) - The message encryption function which encrypts an inputted character vector *plaintext* using the inputted public key(*e*, *n*) and outputs the character vector *ciphertext.*

-   RSADecrypt(*ciphertext*, *d*, *n*) - The message decryption function which decrypts an inputted character vector *ciphertext* using the inputted private key(*d*, *n*) and outputs the character vector *plaintext.*
