---
title: "README"
author: "Henry Hu"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

<!-- badges: start -->

[![R-CMD-check](https://github.com/Henryhuhuhu/RPackage/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/Henryhuhuhu/RPackage/actions/workflows/R-CMD-check.yaml) [![Codecov test coverage](https://codecov.io/gh/Henryhuhuhu/RPackage/branch/main/graph/badge.svg)](https://app.codecov.io/gh/Henryhuhuhu/RPackage?branch=main)

<!-- badges: end -->

## Installation instructions

To install this package from GitHub to Rstudio, RTools and devtools are required to be installed. Run the following code on the Console.

```{r}
devtools::install_github("Henryhuhuhu/RPackage")
```

## RSA Package

Data encryption is widely used to secure data while it is transmitted from a sender and receiver. The Rivest, Shamir, Adleman (RSA) algorithm is one of the most secure methods of data encryption that is used today. The reason for this is because of the use of asymmetric keys meaning the key for encryption is not closely related to the key for decryption. The algorithm includes essentially three steps: key generation, encryption and decryption. This R package will include functions that will perform these steps.

-   RSAPrimeGenerate(*n*) - The random prime number generator of an inputted bit size *n* that outputs a prime number of the provided bit size.

-   RSAGenerateKey(*p*, *q*) - The key encryption function which needs the input of two unique large prime integers *p* and *q* to generate the public and private keys. The function would require the inputs of p, q being very large non equivalent prime integers. This would then be passed through primality and other compatibility checks in order to be used to calculate the private and public keys that will be outputted to the sender and receiver respectively. A phi function is calculated by tallying the number of coprime numbers in reference to the product of the inputs (n). Next an integer e is selected from the pool of coprime integers that satisfies 1\<e\<(n) and gcd(e,(n)) = 1. The public key is then generated using the values of e and n. The private key is generated by calculating d such that d\*e % (n) =1 . As a result, there can be multiple solutions to e and d.

-   RSAEncrypt(*plaintext*, *e*, *n*) - The message encryption function which encrypts an inputted character vector *plaintext* using the inputted public key(*e*, *n*) and outputs the character vector *ciphertext.* The *plaintext* is first converted into a numerical value. The package will refer to using the ASCII values to represent the *plaintext* in order to account for a large variety of characters. The encryption of each character is then calculated as c = m \^ e % n where m is the ASCII value of a character and c is the encrypted character (output).

-   RSADecrypt(*ciphertext*, *d*, *n*) - The message decryption function which decrypts an inputted character vector *ciphertext* using the inputted private key(*d*, *n*) and outputs the character vector *plaintext.* The decrypting process will essentially work backwards from the encryption function. First it will find the ASCII values m = c \^ d % n . then it will convert the ASCII values into characters and output the *plaintext*.
